### 2017-02-14 R/cambridge.Rmd
Testing original csv files

fileNamesList <- list(
    activeTransportTimeFile = "~/GHI/misc/activeTransportTime.csv",
    roadInjuriesFile = "~/GHI/misc/stata19.csv",
#    roadInjuriesFile = "~/GHI/misc/roadInjuries.csv",
    GBDFile = "~/GHI/misc/gbdEngland_20170209.csv"
#    GBDFile = "~/GHI/misc/gbd.csv"
)

>>>>

fileNamesList <- list(
    activeTransportTimeFile = "~/GHI/misc/activeTransportTime.csv",
#    roadInjuriesFile = "~/GHI/misc/stata19.csv",
    roadInjuriesFile = "~/GHI/misc/roadInjuries.csv",
#    GBDFile = "~/GHI/misc/gbdEngland_20170209.csv"
    GBDFile = "~/GHI/misc/gbd.csv"
)
